---
title: "Validation and testing"
author: "Amanda White"
date: "2026-04-25"
output: html_document
---

```{r}
#Reading in saved files
IL_reviews <- readr::read_csv("/Users/amandawhite/Downloads/IL_reviews15_20_ISA401_yes.csv")
moon_df <- readr::read_csv("/Users/amandawhite/Downloads/moon_df_yes.csv")
STE <- readr::read_csv("/Users/amandawhite/Downloads/reviews_STE.csv")
weather_df <- readr::read_csv("/Users/amandawhite/Downloads/weather_df_yes.csv")
```

```{r}
#Joining weather and reviews
weather_review <- IL_reviews |>
  left_join(weather_df, by = c("review_date", "latitude", "longitude"))
```

```{r}
#Joining moon phases
moon_weather_review <- weather_review |>
  left_join(moon_df, by = "review_date")
```

```{r}
#Joining STE
final_df <- moon_weather_review |>
  left_join(STE, by = "review_id")
```

```{r}
#Renaming stars column for better data understanding
final_df <- final_df |>
  rename(
    stars_review = stars.x,
    stars_business = stars.y
  )
```

```{r}
# Checking for duplicates
final_df |>
  count(review_id) |>
  filter(n > 1)
```
None! Yay

```{r}
# Check for missing
colSums(is.na(final_df))
```
No missing in important columns


```{r}
write.csv(final_df, "final_df_401.csv", row.names = FALSE)
```


```{r}
final_df <- readr::read_csv("/Users/amandawhite/Downloads/final_df_401.csv")
```


```{r}
# Summary statistics
library(tidyverse)
final_df |>
  group_by(phase) |>
  summarise(
    proportion = mean(review_weird, na.rm = TRUE),
    weird_count = sum(review_weird, na.rm = TRUE),
    total = n()
  )
```

```{r}
# Testing significance of moon phase and weird reviews
tab <- table(final_df$phase, final_df$review_weird)
chisq.test(tab)
```
Not significant :(

```{r}
# Testing significance of moon phase and stars
anova <- aov(stars_review~phase, data = final_df)
summary(anova)
```

Not significant :(

```{r}
# Testing significance of moon phase and review intensity
anova1 <- aov(review_intensity~phase, data = final_df)
summary(anova1)
```
Wooo significant, so let's take a further look using Tukey's test

```{r}
TukeyHSD(anova1)
```

Statistical difference between New moon and Full Moon, and New Moon and Last Quarter (at alpha = .1) with New Moon having less intense reviews for both.

```{r}
# Seeing if there are some businesses that don't have a lot of reviews and a few were classified as "weird"
final_df |>
  group_by(phase, business_id) |>
  summarise(
    proportion = mean(review_weird, na.rm = TRUE),
    count = n(),
    .groups = "drop"
  ) |>
  filter(proportion > 0.2, count < 10)
```

This is mildly concerning. It might be altering my results that 682 businesses don't have enough reviews to balance out the one's classified as weird.


## Let's look to see if precipitation makes any difference

```{r}
t.test(precipitation ~ review_weird, data = final_df)
```
Not significant

```{r}
mod <- lm(stars_review ~ precipitation, data = final_df)
summary(mod)
```
Not significant


```{r}
mod1 <- lm(review_intensity ~ precipitation, data = final_df)
summary(mod1)
```
 Not significant


```{r}
# Maybe a discrete variable will show significance?
final_df <- final_df |>
  dplyr::mutate(
    rain = ifelse(precipitation > 0, 1, 0)
  )
```

```{r}
final_df |>
  group_by(rain) |>
  summarise(
    avg_stars = mean(stars_review, na.rm = TRUE),
    count = n()
  )
```


```{r}
t.test(stars_review ~ rain, data = final_df)
```

Very interesting that when there is precipitation reviews are more positive. 


```{r}
t.test(review_intensity ~ rain, data = final_df)
```
But, reviews are not more intense.

```{r}
tab1 <- table(final_df$rain, final_df$review_weird)
chisq.test(tab1)
```
And not more weird.

## Now let's look at moon phase and rain

```{r}
mod1 <- lm(stars_review~rain + phase, data = final_df)
summary(mod1)
```
Rain is still significant

```{r}
#Checking interaction between moon and rain
mod2 <- lm(stars_review~rain * phase, data = final_df)
summary(mod2)
```

Well, looks like there is no significance of rain across moon phases, or at all. The effect was likely noise and should not be read into. 


```{r}
#Just to be sure
mod3 <- lm(stars_review~precipitation * phase, data = final_df)
summary(mod3)
```
Matches up.


## Lets check the interactions on review intensity

```{r}
mod3 <- lm(review_intensity~rain * phase, data = final_df)
summary(mod3)
```

Slight interaction on rain:FullMoon, but probably noise.

```{r}
mod4 <- lm(review_intensity~precipitation * phase, data = final_df)
summary(mod4)
```

Now this is interesting. 

## Trying for weird reviews

```{r}
mod5 <- glm(review_weird ~ precipitation * phase, 
    data = final_df, 
    family = "binomial")
summary(mod5)
```
Nothing.


```{r}
mod6 <- glm(review_weird ~ rain * phase, 
    data = final_df, 
    family = "binomial")
summary(mod6)
```

Nothing here either.
