---
title: "Weather"
author: "Amanda White"
date: "2026-04-07"
output: html_document
---

Sometimes weather can have an effect on people's moods. In order to control for weather related factors I am working with the Open Meteo API to grab high and low temperatures and total precipitation. The data I am using is from Illinois, so the snow might make people more irritable than normal, which effects my analysis.


```{r}
#Reading in saved file
IL_reviews <- readr::read_csv("/Users/amandawhite/Downloads/IL_reviews15_20_ISA401_yes.csv")
```


```{r}
#Gathering unique locations and dates to call the weather api
library(dplyr)
weather_keys <- IL_reviews |>
  distinct(latitude, longitude, review_date)
```


```{r}
library(httr2)
library(dplyr)
library(jsonlite)

#Weather function
get_weather <- function(lat, lon, date) {
  
  #Used this to be nice and not hit the 600 calls/minute API limit
  Sys.sleep(.12)
  
  url <- "https://archive-api.open-meteo.com/v1/archive"
  
  request <- request(url) |>
    req_url_query(
      latitude = lat,
      longitude = lon,
      start_date = date,
      end_date = date,
      daily = "temperature_2m_max,temperature_2m_min,precipitation_sum",
      timezone = "auto",
      temperature_unit = "fahrenheit"
    )
  
  response <- request |> req_perform()
  
  data <- response |> resp_body_json()
  
  #Making data frame
  tibble(
    review_date = as.Date(date),
    latitude = lat,
    longitude = lon,
    temp_max = data$daily$temperature_2m_max[[1]],
    temp_min = data$daily$temperature_2m_min[[1]],
    precipitation = data$daily$precipitation_sum[[1]]
  )
}

```

```{r}
#Testing the function
get_weather(
  lat = il_reviews3$latitude[1],
  lon = il_reviews3$longitude[1],
  date = il_reviews3$review_date[1]
)
# IT WORKED!
```

I have to run this code chunk below in batches because of the API limits. I ran batches of 5000 calls twice a day (since the limit is 10000 calls/day and 5000 calls/hour). This is the final chunk, I would just adjust which rows I was calling.

```{r}
library(purrr)
#Collecting the weather data
weather_df7 <- map_df(
  30000:30694,
  ~ get_weather(
      lat = weather_keys$latitude[.x],
      lon = weather_keys$longitude[.x],
      date = weather_keys$review_date[.x]
    )
)
```

```{r}
write.csv(weather_df7, "weather_df7.csv", row.names = FALSE)
```

```{r}
weather_df1 <- readr::read_csv("/Users/amandawhite/weather_df1.csv")
weather_df2 <- readr::read_csv("/Users/amandawhite/weather_df2.csv")
weather_df3 <- readr::read_csv("/Users/amandawhite/Downloads/weather_df3.csv")
weather_df3.5 <- readr::read_csv("/Users/amandawhite/Downloads/weather_df3_5.csv")
weather_df4 <- readr::read_csv("/Users/amandawhite/Downloads/weather_df4.csv")
weather_df5 <- readr::read_csv("/Users/amandawhite/Downloads/weather_df5.csv")
weather_df6 <- readr::read_csv("/Users/amandawhite/Downloads/weather_df6.csv")
weather_df7 <- readr::read_csv("/Users/amandawhite/Downloads/weather_df7.csv")
```

```{r}
#Making combined weather df
weather_df <- dplyr::bind_rows(weather_df1, weather_df2, weather_df3, weather_df3.5, weather_df4, weather_df5, weather_df6, weather_df7)
```

```{r}
#Making sure we got all of them
nrow(weather_df)-nrow(weather_keys)
```

```{r}
write.csv(weather_df, "weather_df_yes.csv", row.names = FALSE)
```
